Visualization and analysis of probability distributions of large temporal data

### 2021-11-17 Rmd/04-gracsr.Rmd
dunn index reference update

Different approaches to determining number of clusters are required for varied applications and research objectives. It is often beneficial to investigate numerous cluster statistics in order to arrive at a number of clusters, since clustering has a variety of objectives (e.g., between-cluster separation, within-cluster homogeneity, representation by centroids, etc.), which could be in conflict with one another. Some typical ways of determining the number of clusters in the literature (e.g., the gap statistic [@tibshirani2001estimating], average silhouette width [@rousseeuw1987silhouettes], Dunn index [@dunn1973fuzzy]) are inspired by defining and balancing "within-cluster homogeneity" and "between-cluster separation". The Cluster separation index ($sindex$) proposed by @Hennig2014-ah is used as a guide to select the number of clusters in Section \ref{sec:validation}. $sindex$ [@R-fpc] is a compromise between minimum cluster separation and average cluster separation and is less sensitive to a single or few ambiguous points. $sindex$ cannot be optimized over the number of clusters, since increasing the number of clusters reduces it. The number of clusters required is determined by the slope going from steep to shallow (an elbow).

>>>>

Different approaches to determining number of clusters are required for varied applications and research objectives. It is often beneficial to investigate numerous cluster statistics in order to arrive at a number of clusters, since clustering has a variety of objectives (e.g., between-cluster separation, within-cluster homogeneity, representation by centroids, etc.), which could be in conflict with one another. Some typical ways of determining the number of clusters in the literature (e.g., the gap statistic [@tibshirani2001estimating], average silhouette width [@rousseeuw1987silhouettes], Dunn index [@Dunn1973-gk]) are inspired by defining and balancing "within-cluster homogeneity" and "between-cluster separation". The Cluster separation index ($sindex$) proposed by @Hennig2014-ah is used as a guide to select the number of clusters in Section \ref{sec:validation}. $sindex$ [@R-fpc] is a compromise between minimum cluster separation and average cluster separation and is less sensitive to a single or few ambiguous points. $sindex$ cannot be optimized over the number of clusters, since increasing the number of clusters reduces it. The number of clusters required is determined by the slope going from steep to shallow (an elbow).
